Make maps of loan words

### 2025-03-19 analysis/paper/paper.qmd
update paper code
add reference

---
title: "Loan word maps"
author:
  - Henning Schreiber:
      correspondence: "yes"
      email: janedoe@fosg.org
      orcid: 0000-0003-1689-0557
      institute: uhh

@@

# Creating language maps

Read location data from glottolog and Sahelia databases

@@

@@

The data contains certain duplicate entries. These need to be removed to avoid overly full plots
```{r clean duplicates}
# Function to remove duplicates
remove_duplicates <- function(df_list) {
  df_list <- lapply(df_list, function(df) {
    df <- df |> 
      dplyr::distinct(glott_code, form, .keep_all = TRUE)
    return(df)
  })
  return(df_list)
}

@@

Save an html version of all objects
```{r}
#| label: save-maps
#| eval: false
save_maps(data_list, background = "bw")
```

```{r}
#| label: fig-demo-plot
#| fig-cap: "A plot of random numbers"
plot(rnorm(10))
```

@fig-demo-plot shows how we can have a caption and cross-reference for a plot. Note that figure label and cross-references must both be prefixed with `fig-`

```{r}
#| label: demo-inline-code
#| echo: false
x <- round(pi, 2)
```

Here is an example of inline code `r x` in the middle of a sentence.

# Discussion

# Conclusion

# Acknowledgements

>>>>

---
title: "Make maps of loan words"
author:
  - Henning Schreiber:
      correspondence: "yes"
      email: janedoe@fosg.org
      orcid: 0000-0003-1689-0557
      institute: uhh

@@

In order to have location data, we read in the African languages, their glottoglog code, and their location from the glottolog database (@hammarstromGlottolog2024).

@@

Next, we read in the data and join the entries to the glottolog entries. Modify the list of .csv files to suit your interests. If you want to upload new files, place these in the directory /analysis/data/raw_data.Make sure any new data has a glottolog language code in a varaible named "glott_code"

@@

The data may contain certain duplicate entries. These need to be removed to avoid overly full plots. This is done by running the code below.
```{r clean duplicates}
# Function to remove duplicates
remove_duplicates <- function(df_list) {
  df_list <- lapply(df_list, function(df) {
    df <- df |> 
      dplyr::distinct(glott_code, form, .keep_all = TRUE)
    return(df)
  })
  return(df_list)
}

@@

Save an html version of all objects
```{r}
#| label: save-maps
#| eval: false
#save_maps(data_list, background = "bw")

#create_leaflet_map(data_list[[2]])
```
